---
title: "Zelizer (2019) Paper Replication and Extension"
author: "Miroslav Bergam"
date: "4/14/2020"
output: bookdown::pdf_document2
bibliography: bibliography.bib
link_citations: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#### Load libraries
library(plyr)
library(stringr)
library(ggplot2)
library(boot)
library(tidyr)
library(grid)
library(RColorBrewer)
library(bookdown)
library(reshape2)
library(grid)
library(gridExtra)
library(data.table)
library(blockTools)
library(dplyr)
library(Hmisc)
library(gt)
library(rstanarm)

```

```{r Import Data}

load("Cue-taking/zelizer_replication_data_IPC.RData")

df$t <- relevel(as.factor(df$t) , ref = 2) ### Relevel factors so control is base category; Direct treatment: -1 is advocate; 0 is control; 1 is staffer
df$t.spill <- relevel(as.factor(df$t.spill) , ref = 2) ### Indirect treatment:  -1 is advocate; 0 is control; 1 is staffer; 2 is double staffer
for(i in 1:ncol(t.for.ri)){
  t.for.ri[,i] <- relevel(as.factor(t.for.ri[,i]) , ref = 2)
  t.spill.for.ri[,i] <- relevel(as.factor(t.spill.for.ri[,i]) , ref = 2)
  #cat("\r", i, "of", ncol(t.for.ri)) ### How far loop has progressed
}
df$treatment <- interaction(df$t,df$t.spill)
levels(t.for.ri[,1])
levels(t.spill.for.ri[,1])
levels(df$treatment)

```

## Abstract

Zelizer (2019) finds that the cues that legislators take from their peers, in
addition to other credible sources of information like briefings, influence
their policymaking decisions. I succesfully replicated Zelizer’s results.
Zelizer took a Bayesian approach to his findings, running 10,000 simulations for
each table and figure using for-loops to produce estimates and standard
deviations; however, this made his code inefficient and extremely slow Using the
rstanarm package, I was able to simplify his code while maintaining the Bayesian
integrity of the study. This extension served as both a robustness test of his
results and a simplification that makes the study more easily reproducable.

## Literature Review

Studies as early as Matthews and Stimson (1975) and Kingdon (1973) find that
cue-taking has a large influence on the decisions made by policy-makers. Kingdon
concluded that cue-taking influences around 40% of decisions while Matthews and
Stimsonn pinned the number a 75%. More recent observational studies like Masket
(2008) found the percentage of votes influenced by cue-taking to be 10%. Masket
found that information was shared primarily through deskmates, while Matthews
and Stimson found that it wa shared between friends. Coppock (2014) found that
information wa shared between ideologically-similar legislators. This paper
abets the conclusion that cue-taking influences policy decisions while updating
the approach and contributing a new layer of findings. It uses a large dataset
from two legislative field experiments, lending it power that previous studies
may have lacked, and focuses on legislators who share office suites. The paper
contributes the findings that that cues complement complement rather than
substitute other sources of expertise as well as that cue-making's influence
occurs late in the decision-making process.

^[[All analysis for this paper is availible at https://github.com/mirobergam/Replication-paper](https://github.com/mirobergam/Replication-paper)]


## Figures 
### Table 3

```{r Table 3}

### Table 3:
table3 <- subset(df , office.size > 1) %>%
  ddply(. , .(treatment) , function(x) out = data.frame(
    Weighted.Mean = round(weighted.mean(x$cosp , x$ipw),3) ,
    N = length(x$cosp))) %>%
  mutate(treatment = as.integer(treatment)) %>%
  filter(treatment == 1 | treatment == 3 | treatment == 7 | treatment == 9)

treatments3 <- tibble(treatment = c(1,3,7,9),
                      `Cue-Taking` = c("NO CUE-TAKING", "NO CUE-TAKING", 
                                       "YES CUE-TAKING", "YES CUE-TAKING"),
                      Briefing = c("NO", "YES", "NO", "YES"))

table3 <- treatments3 %>% left_join(table3, by = "treatment") %>%
  mutate(Weighted.Mean = Weighted.Mean * 100) %>%
  mutate(Weighted.Mean = as.character(Weighted.Mean)) %>%
  mutate(N = as.character(N)) %>%
  mutate(`Mean(N)` = paste(Weighted.Mean," (", N, ")")) %>%
  select(`Cue-Taking`, Briefing, `Mean(N)`)  %>%
  pivot_wider(names_from = `Cue-Taking`, values_from = `Mean(N)`)

gt(table3)

```

### Table 4

```{r Table 4, cache = TRUE}

### x <- stan_lm(cosp ~ treatment + bill + leg, data = subset(df , office.size > 1), weights=ipw, refresh = FALSE, prior = NULL)

### summary(x, digits = 10)

## pp_check(model, "dens_overlay") # takes the original data and show in a really dark apttern, and show the bayesian runs of it in the background to see how well the data ftis
# weird fit
# because these are discrete values the model ended up matching up weird but its decent. bayesian model assu,es conntinues. <ike for example the tail extends past 0. try to make it discrete instead of continiuous

# x <- x$coefficients[c('treatment1.0','treatment0.1','treatment1.1')] and do same w ses and bind

# Preferred specification
estimates <- data.frame(itt = matrix(NA,nrow=3,ncol=1))
row.names(estimates) <- c("t","t.spill","t+t.spill")

## Create new dataset

estimates[1:3,] <- summary(lm(cosp ~ treatment + bill + leg ,
                              data = subset(df , office.size > 1),
                              weights=ipw))$coef[
                              c('treatment1.0','treatment0.1','treatment1.1'),
                              'Estimate']

estimates[2,1]/estimates[1,1] ### Contagion rate
nrow(subset(df , office.size > 1))

################################

ri.t <- data.frame(matrix(NA, nrow = 3 , ncol = 100)) ##this used to be 10,000
row.names(ri.t) <- row.names(estimates)
ci.t <- ri.t
tempdf <- df

tempdf$Y0 <- df$cosp
tempdf$Y0[tempdf$treatment=="1.0"] <- tempdf$cosp[tempdf$treatment=="1.0"] -
                                            estimates[1,1]
tempdf$Y0[tempdf$treatment=="0.1"] <- tempdf$cosp[tempdf$treatment=="0.1"] -
                                            estimates[2,1]
tempdf$Y0[tempdf$treatment=="1.1"] <- tempdf$cosp[tempdf$treatment=="1.1"] -
                                            estimates[3,1]

for(i in 1:ncol(ri.t)){
  tempdf$t <- t.for.ri[,i]
  tempdf$t.spill <- t.spill.for.ri[,i]
  tempdf$ipw <- ipw.for.ri[,i]
  tempdf$treatment <- interaction(tempdf$t,tempdf$t.spill)

  ri.t[1:3,i] <- summary(lm(cosp ~ treatment + bill + leg ,
                            data = subset(tempdf , office.size > 1),
                            weights=ipw))$coef[
                            c('treatment1.0','treatment0.1','treatment1.1'),
                            'Estimate']

  tempdf$cosp1 <- tempdf$Y0
  tempdf$cosp1[tempdf$treatment=="1.0"] <- tempdf$Y0[tempdf$treatment=="1.0"] +
                                                estimates[1,1]
  tempdf$cosp1[tempdf$treatment=="0.1"] <- tempdf$Y0[tempdf$treatment=="0.1"] +
                                                estimates[2,1]
  tempdf$cosp1[tempdf$treatment=="1.1"] <- tempdf$Y0[tempdf$treatment=="1.1"] +
                                                estimates[3,1]

  ci.t[1:3,i] <- summary(lm(cosp1 ~ treatment + bill + leg ,
                            data = subset(tempdf , office.size > 1),
                            weights=ipw))$coef[
                            c('treatment1.0','treatment0.1','treatment1.1'),
                            'Estimate']
  #cat("\r", i, "of", ncol(ri.t)) ### How far loop has progressed
}

########################## 


#### Table 4:
table4 <- apply(cbind.data.frame(ri.t[1:3,], estimates) , 1 , function(x)
  out = unlist(data.frame(
    Est = round(x[ncol(ri.t)+1],3),
#    mean.sim.ITT = round(mean(x[1:ncol(ri.t)]),4),
    SE = round(sd(x[1:ncol(ri.t)]),3)
#    p.one.sided = round(mean(x[1:ncol(ri.t)] > x[ncol(ri.t)+1]),4)
  )))

table4 <- as_tibble(table4)

table4 <- table4 %>%
  mutate(t = t * 100,
         t.spill = t.spill * 100, 
         `t+t.spill` = `t+t.spill` * 100) %>%
  mutate(Value = c("ITT", "SE"),
         Briefing = t,
        `Cue-Taking` = t.spill, 
        Combined = `t+t.spill`) %>%
  select(Value, Briefing, `Cue-Taking`,Combined)

gt(table4)

```

### Table 5

```{r Table 5, cache = TRUE}

estimates <- data.frame(itt = matrix(NA,nrow=3,ncol=2))
row.names(estimates) <- c("t","t.spill","t+t.spill")
colnames(estimates) <- c("no_vote","vote")

estimates[1:3,1] <- unlist(summary(lm(cosp ~ treatment + bill + leg,
                                      data = subset(df , office.size > 1 & passed==0),
                                      weights=ipw))$coef[c('treatment1.0',
                                                           'treatment0.1',
                                                           'treatment1.1'),
                                                           'Estimate'])


estimates[1:3,2] <- unlist(summary(lm(cosp ~ treatment + bill + leg,
                                      data = subset(df , office.size > 1 & passed==1),
                                      weights=ipw))$coef[c('treatment1.0',
                                                           'treatment0.1',
                                                           'treatment1.1'),
                                                           'Estimate'])

#######################               RI           ##########################

ri.t3 <- array(NA, dim = c(3 , 2, ncol(t.spill.for.ri)),
               dimnames = list(
                 c("t","t.spill","t+t.spill"),
                 c("no_vote","vote"),
                 c(1:10000)))

for(i in 1:ncol(t.spill.for.ri)){ #
  tempdf <- df[,c("bill","cosp","office.size","leg","passed")]
  tempdf$t <- t.for.ri[,i]
  tempdf$t.spill <- t.spill.for.ri[,i]
  tempdf$ipw <- ipw.for.ri[,i]

  tempdf$treatment <- interaction(tempdf$t,tempdf$t.spill)
  ri.t3[1:3,1,i] <- unlist(summary(lm(cosp ~ treatment + bill + leg,
                                      data = subset(tempdf , office.size > 1 & passed==0),
                                      weights=ipw))$coef[c('treatment1.0',
                                                           'treatment0.1',
                                                           'treatment1.1'),
                                                           'Estimate'])

  ri.t3[1:3,2,i] <- unlist(summary(lm(cosp ~ treatment + bill + leg,
                                      data = subset(tempdf , office.size > 1 & passed==1),
                                      weights=ipw))$coef[c('treatment1.0',
                                                           'treatment0.1',
                                                           'treatment1.1'),
                                                           'Estimate'])

  #cat("\r", i, "of", ncol(t.spill.for.ri)) ### How far loop has progressed
}

### Table 5:
for(j in 1:2){
  print(colnames(estimates)[j])
  for(i in 1:3){
    print(row.names(estimates)[i])
    assign(paste0("cat", i * (j+4)), 
    data.frame(
      Est = estimates[i,j] ,
      SD = sd(ri.t3[i,j,])
    ))
  }}

table5 <- rbind(cat5, cat10, cat15, cat6, cat12, cat18) %>%
  mutate(`Reached Floor?` = c("Bills that failed in committee",
                              "Bills that failed in committee",
                              "Bills that failed in committee",
                              "Bills that reached floor",
                              "Bills that reached floor",
                              "Bills that reached floor"),
         Condition = c("Briefing","Cue-Taking","Combined",
                       "Briefing","Cue-Taking","Combined"),
         ITT = round((Est * 100),3),
         SE = round((SD * 100),3)) %>%
  mutate(ITT = as.character(ITT)) %>%
  mutate(SE = as.character(SE)) %>%
  mutate(`ITT(SE)` = paste(ITT," (", SE, ")")) %>%
  select(`Reached Floor?`, Condition, `ITT(SE)`)  %>%
  pivot_wider(names_from = `Reached Floor?`, values_from = `ITT(SE)`)

gt(table5)

```

### Table 6

```{r Table 6, cache = TRUE}

### This function creates simulation-based inverse probability weights.
ipw.function <- function(DATASET , T , T.SPILL , RI.T , RI.T.SPILL , VARNAME){
	temp <- apply(matrix(1:ncol(RI.T.SPILL) , nrow=1) , 2 , function(z) {
		temp1 <- as.numeric(RI.T.SPILL[,z]==DATASET[,T.SPILL])
		temp2 <- as.numeric(RI.T[,z]==DATASET[,T])
		return(as.numeric(temp1+temp2==2))
	})

	DATASET$V1 <- 1/apply(temp , 1 , mean)
	setnames(DATASET,"V1",VARNAME)
	return(DATASET)
}

load("Cue-taking/replication_data_alternative_spillover_simulations.RData")
### Add IPWs for observed assignments
df <- ipw.function(df , "t" , "t.spill.desk" , t.for.ri , ri.t.spill.desk , "ipw.desk")
df <- ipw.function(df , "t" , "t.spill.dist" , t.for.ri , ri.t.spill.dist , "ipw.dist")
df <- ipw.function(df , "t" , "t.spill.ideo" , t.for.ri , ri.t.spill.ideo , "ipw.ideo")

table(df$t.spill,useNA="always")
table(df$t.spill.desk,useNA="always")
table(df$t.spill.dist,useNA="always")
table(df$t.spill.ideo,useNA="always")

df$treatment.desk <- relevel(interaction(df$t,df$t.spill.desk) , ref = 4)
df$treatment.dist <- relevel(interaction(df$t,df$t.spill.dist) , ref = 4)
df$treatment.ideo <- relevel(interaction(df$t,df$t.spill.ideo) , ref = 4)

estimates <- data.frame(itt = matrix(NA,nrow=3,ncol=4))
row.names(estimates) <- c("t","t.spill","t+t.spill")
colnames(estimates) <- c("office","desk","distance","ideology")

### Office Spillover
estimates[1:3,1] <- unlist( summary(lm(cosp ~ treatment + bill + leg,
                      data = subset(df , office.size > 1 &
                                      !is.na(t.spill.desk) &
                                      !is.na(t.spill.dist) &
                                      !is.na(t.spill.ideo)),
                      weights=ipw))$coef[c('treatment1.0',
                                           'treatment0.1',
                                           'treatment1.1'),
                                           'Estimate'] )

### Desk Spillover
estimates[1:3,2] <- unlist( summary(lm(cosp ~ treatment.desk + bill + leg,
                      data = subset(df , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw.desk))$coef[c('treatment.desk1.0',
                                                'treatment.desk0.1',
                                                'treatment.desk1.1'),
                                                'Estimate'] )

 ### Distance Spillover
estimates[1:3,3] <- unlist( summary(lm(cosp ~ treatment.dist + bill + leg,
                      data = subset(df , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw.dist))$coef[c('treatment.dist1.0',
                                                'treatment.dist0.1',
                                                'treatment.dist1.1'),
                                                'Estimate'] )

### Ideology Spillover
estimates[1:3,4] <- unlist( summary(lm(cosp ~ treatment.ideo + bill + leg,
                      data = subset(df , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw.ideo))$coef[c('treatment.ideo1.0',
                                                'treatment.ideo0.1',
                                                'treatment.ideo1.1'),
                                                'Estimate'] )

#######################               RI           ##########################

ri.t2 <- array(NA, dim = c(3 , 4, 50), #originally ncol(ri.t.spill.desk)
               dimnames = list(
                 c("t","t.spill","t+t.spill"),
                 c("office","desk","distance","ideology"),
                 c(1:50)))

for(i in 1:25){ #ncol(ri.t.spill.desk
  tempdf <- df[,c("bill","cosp","office.size","leg")]
  tempdf$t <- t.for.ri[,i]
  tempdf$t.spill <- t.spill.for.ri[,i]
  tempdf$ipw <- ipw.for.ri[,i]

  tempdf$t.spill.desk <- ri.t.spill.desk[,i]
  tempdf$t.spill.dist <- ri.t.spill.dist[,i]
  tempdf$t.spill.ideo <- ri.t.spill.ideo[,i]


  tempdf <- ipw.function(tempdf , "t" , "t.spill.desk" , t.for.ri , ri.t.spill.desk , "ipw.desk")
  tempdf <- ipw.function(tempdf , "t" , "t.spill.dist" , t.for.ri , ri.t.spill.dist , "ipw.dist")
  tempdf <- ipw.function(tempdf , "t" , "t.spill.ideo" , t.for.ri , ri.t.spill.ideo , "ipw.ideo")
  tempdf$treatment <- interaction(tempdf$t,tempdf$t.spill)
  tempdf$treatment.desk <- interaction(tempdf$t,tempdf$t.spill.desk)
  tempdf$treatment.dist <- interaction(tempdf$t,tempdf$t.spill.dist)
  tempdf$treatment.ideo <- interaction(tempdf$t,tempdf$t.spill.ideo)
  #print(levels(tempdf$treatment.ideo)[1])
  #print(levels(tempdf$treatment.desk)[1])
  #print(levels(tempdf$treatment.dist)[1])

  ### Office Spillover
  ri.t2[1:3,1,i] <- unlist( summary(lm(cosp ~ treatment + bill + leg,
                      data = subset(tempdf , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw))$coef[c('treatment1.0',
                                           'treatment0.1',
                                           'treatment1.1'),
                                           'Estimate'] )

  ### Desk Spillover
  ri.t2[1:3,2,i] <- unlist( summary(lm(cosp ~ treatment.desk + bill + leg,
                      data = subset(tempdf , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw.desk))$coef[c('treatment.desk1.0',
                                                'treatment.desk0.1',
                                                'treatment.desk1.1'),'Estimate'] )

  ### Distance Spillover
  ri.t2[1:3,3,i] <- unlist( summary(lm(cosp ~ treatment.dist + bill + leg,
                      data = subset(tempdf , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw.dist))$coef[c('treatment.dist1.0',
                                                'treatment.dist0.1',
                                                'treatment.dist1.1'),
                                                'Estimate'] )

  ### Ideology Spillover
  ri.t2[1:3,4,i] <- unlist( summary(lm(cosp ~ treatment.ideo + bill + leg,
                      data = subset(tempdf , office.size > 1 &
                                     !is.na(t.spill.desk) &
                                     !is.na(t.spill.dist) &
                                     !is.na(t.spill.ideo)),
                      weights=ipw.ideo))$coef[c('treatment.ideo1.0',
                                                'treatment.ideo0.1',
                                                'treatment.ideo1.1'),
                                                'Estimate'] )

  #cat("\r", i, "of", ncol(ri.t.spill.desk)) ### How far loop has progressed
}

### Table 6:
for(j in 1:4){
  print(colnames(estimates)[j])
  for(i in 1:3){
  print(row.names(estimates)[i])
  assign(paste0("owl", i * (j+6)), 
  data.frame(
  	 st = estimates[i,j] ,
  	SD = sd(ri.t2[i,j,])
  ))
  }}

table6 <- rbind(owl7, owl8, owl9, owl10, owl14, owl16,
                owl18, owl20, owl21, owl24, owl27, owl30) %>%
  mutate(Condition = c("Briefing","Briefing","Briefing","Briefing",
                       "Cue-Taking","Cue-Taking","Cue-Taking","Cue-Taking",
                       "Combined", "Combined", "Combined", "Combined"),
         Model = c("Offices", "Desks", "Districts", "Ideology",
                   "Offices", "Desks", "Districts", "Ideology",
                   "Offices", "Desks", "Districts", "Ideology"),
         ITT = round((st * 100),3),
         SE = round((SD * 100),3)) %>%
  select(Model, Condition, ITT, SE)

table61 <- table6 %>%
  mutate(ITT = as.character(ITT)) %>%
  mutate(SE = as.character(SE)) %>%
  mutate(`ITT(SE)` = paste(ITT," (", SE, ")")) %>%
  select(Model, Condition, `ITT(SE)`)  %>%
  pivot_wider(names_from = Model, values_from = `ITT(SE)`)

gt(table61)

```


### Figure 3

```{r}

load("Cue-taking/zelizer_replication_data_dates_IPC.RData")

nsims <- 10 #This was at 1000 before

df$treatment <- interaction(df$t,df$t.spill)
levels(df$treatment)

nDays <- seq(0,98,7)
days.ri <- data.frame(matrix(NA,nrow=length(nDays) , ncol = 3))
days.ri.SE <- data.frame(matrix(NA,nrow=length(nDays) , ncol = 3))

for(i in nDays){
  Ydays <- as.numeric(!is.na(df$days) & df$days <= i & df$days >=0 & df$cosp==1)
  days.ri[match(i,nDays),1:3] <- summary(lm(Ydays ~ treatment + bill + leg ,
                                            data = df,
                                            weights=ipw))$coef[c('treatment1.0','treatment0.1','treatment1.1'),'Estimate']
  temp <- data.frame(matrix(NA,nrow=nsims,ncol=3))
  for(j in 1:nsims){
    treatment.sim <- interaction(t.for.ri2[,j],t.spill.for.ri2[,j])
    levels(treatment.sim)
    temp[j,1:3] <- summary(lm(Ydays ~ treatment.sim + bill + leg ,
                              data = df,
                              weights=ipw.for.ri2[,j]))$coef[c('treatment.sim1.0','treatment.sim0.1','treatment.sim1.1'),'Estimate']
  }
  temp <- apply(temp , 2 , sd)
  days.ri.SE[match(i,nDays),1:3] <- temp
  cat("\r", i, "of", nDays) ### How far loop has progressed
}

tempnum <- 1
data.frame(ATE = days.ri[,tempnum],
           CIlow = days.ri[,tempnum] - 1.65*days.ri.SE[,tempnum],
           CIhigh = days.ri[,tempnum] + 1.65*days.ri.SE[,tempnum],
           X = nDays/7) %>%
  ggplot(., aes(x = factor(X) )) +
  geom_errorbar(aes(ymin = CIlow*100 , ymax = CIhigh*100 , width = 0)) +
  geom_point(aes(y = ATE*100)) +
  scale_y_continuous(minor_breaks=waiver(), labels = waiver(), breaks=c(-2,0,2,4,6,8) , limits = c(-2,9)) +
  labs(x = "Week of Session", y = "Est. ATE (perc. pts.)") +
  geom_smooth(aes(y = ATE*100) , col = "black" , method = "loess" , se = FALSE) +
  geom_vline(xintercept=0 , color = "#535353" , lwd = 1) +
  geom_hline(yintercept=0 , color = "#535353" , lwd = 1) +
  theme(panel.background = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_text(color = "#535353" , size = 12, face="bold"),
        axis.title.y = element_text(color = "#535353" , size = 12, face="bold"),
        axis.text.y = element_text(size = 12, colour = "grey50"),
        axis.text.x = element_text(size = 8, colour = "grey50"),
        panel.border = element_blank(),
        legend.key = element_rect(colour = "white",fill = "white"),
        legend.text = element_text(size=10,color="grey50"),
        legend.title = element_text(size = 11, face = "bold", colour = "#535353"),
        strip.text.x = element_text(size = 11, face = "bold", colour = "#535353"),
        strip.background = element_rect(colour = "white", fill = "white"),
        legend.position="right",
        plot.margin = unit(c(0.75,0.75,0.75,0.75), "cm"))


```

### Figure 4

```{r}

tempnum <- 2
data.frame(ATE = days.ri[,tempnum],
           CIlow = days.ri[,tempnum] - 1.65*days.ri.SE[,tempnum],
           CIhigh = days.ri[,tempnum] + 1.65*days.ri.SE[,tempnum],
           X = nDays/7) %>%
  ggplot(., aes(x = factor(X) )) +
  geom_errorbar(aes(ymin = CIlow*100 , ymax = CIhigh*100 , width = 0)) +
  geom_point(aes(y = ATE*100)) +
  scale_y_continuous(minor_breaks=waiver(), labels = waiver(), breaks=c(-2,0,2,4,6,8) , limits = c(-2,9)) +
  labs(x = "Week of Session", y = "Est. ATE (perc. pts.)") +
  geom_smooth(aes(y = ATE*100) , col = "black" , method = "loess" , se = FALSE) +
  geom_vline(xintercept=0 , color = "#535353" , lwd = 1) +
  geom_hline(yintercept=0 , color = "#535353" , lwd = 1) +
  theme(panel.background = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_text(color = "#535353" , size = 12, face="bold"),
        axis.title.y = element_text(color = "#535353" , size = 12, face="bold"),
        axis.text.y = element_text(size = 12, colour = "grey50"),
        axis.text.x = element_text(size = 8, colour = "grey50"),
        panel.border = element_blank(),
        legend.key = element_rect(colour = "white",fill = "white"),
        legend.text = element_text(size=10,color="grey50"),
        legend.title = element_text(size = 11, face = "bold", colour = "#535353"),
        strip.text.x = element_text(size = 11, face = "bold", colour = "#535353"),
        strip.background = element_rect(colour = "white", fill = "white"),
        legend.position="right",
        plot.margin = unit(c(0.75,0.75,0.75,0.75), "cm"))

```

### Bibliography

@main_paper @side_paper_1 @side_paper_2 @side_paper_3 @side_paper_4
